Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Updated Experiments

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that an NA-CTFP (i.e. a path $m$ which satisfies Def.~\ref{def::NACTFP}) exists. Finally, we show that NA-CTFP reaches a fixed point when
  NA Games are zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

@@

>>>>

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that an NA-CTFP (i.e. a path $m$ which satisfies Def.~\ref{def::NACTFP}) exists. Finally, we show that any NA-CTFP reaches a fixed point when
  NA Games are zero-sum and that, when the network has no self-loops
  (i.e., $w^{\mu \mu} = 0$ for all agents $\mu$), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

@@

	In this section, we investigate NA-CTFP through numerical experiments. In particular, we look beyond zero-sum NA games and show that learning on an NA game can lead to periodic behaviour, rather than convergence to a fixed point. In addition, we aim to understand the behaviour of agents learning through NA-CTFP, when the measurements on their reference signal $\refmu$ is corrupted with noise.
